Symmetric Circuits for Rank Gates

### 2018-04-02 sections/conclusion.tex
Fixed a few typos in the symmetric-circuits section and in the conclusion.

The circuit model we have developed is novel, and as such there are many basic
questions of interest. We do not know, for example, whether for each $a \in
\nats$ there is a symmetric circuit with symmetric gates where each gate has
fan-in less than $a$ that computes $\NAND[a+1]$. For a basis $\BB$ let $Q_\BB$
be the set of all queries computed by $\PT$-uniform families of transparent
symmetric circuits defined over $\BB$. We have that $Q_{\MB} \subsetneq
Q_{\RB}$. It follows from Theorem~\ref{} that if $\BB$ is a symmetric basis then
$Q_\BB \subseteq Q_\MB$. It follows that $Q_\MB$ is a basis including structured
functions defined over a vocabulary with two sorts that defines a circuit model
strictly more powerful than any defined by basis of that only include functions
with one sort.s

@@

It is not hard to show that $Q_\BB \subseteq Q_\MB$ for any matrix-symmetric
basis $Q_\BB$ consisting of polynomial-time computable functions if, and only
if, $\FPR$ captures $\PT$.

>>>>

The circuit model we have developed is novel, and as such there are many basic
questions of interest. We do not know, for example, whether for each $a \in
\nats$ there is a symmetric circuit with symmetric gates where each gate has
fan-in less than $a$ that computes $\NAND[a+1]$. For a basis $\BB$ let $Q_\BB$
be the set of all queries computed by $\PT$-uniform families of transparent
symmetric circuits defined over $\BB$. We have that $Q_{\BM} \subsetneq
Q_{\RB}$. It follows from Theorem~\ref{} that if $\BB$ is a symmetric basis then
$Q_\BB \subseteq Q_{\BM}$. It follows that $Q_{\BM}$ is a basis including structured
functions defined over a vocabulary with two sorts that defines a circuit model
strictly more powerful than any defined by basis of that only include functions
with one sort.s

@@

It is not hard to show that $Q_\BB \subseteq Q_{\BM}$ for any matrix-symmetric
basis $Q_\BB$ consisting of polynomial-time computable functions if, and only
if, $\FPR$ captures $\PT$.

### 2018-04-02 sections/symmetric-circuits.tex
Fixed a few typos in the symmetric-circuits section and in the conclusion.

\begin{definition}[Circuits on Structures]
  Let $\mathbb{B}$ be a basis and $\rho$ be a relational vocabulary, we define a
  \emph{$(\mathbb{B}, \rho)$-circuit} $C$ of order $n$ computing a $q$-ary query
  $Q$ as a structure $\langle G, \Omega, \Sigma, \Lambda, L \rangle$.
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G$ is called the set of gates of
    $C$.% and $\vert C \vert := \vert G \vert$.
  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
    constant function mapping to a single output gate.
  \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \rho \uplus
    \{0,1\} $ such that $\vert \Sigma^{-1} (0) \vert \leq 1$ and $\vert
    \Sigma^{-1} (1) \vert \leq 1$. Those gates mapped to $\rho \uplus \{0,1\}$
    are called input gates, with those mapped to $\rho$ called relational gates
    and those mapped to $\{0,1\}$ called constant gates. Those gates mapped to
    $\mathbb{B}$ are called internal gates.
  \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R_i})_{R_i \in
      R}$ such that $\Lambda_{R_i}$ maps each relational gate $g$ with $\Sigma
    (g) = R_i$ to the tuple $\Lambda_{R_i} (g) \in [n]^{r}$. When no ambiguity
    arises we write $\Lambda (g)$ for $\Lambda_{R_i} (g)$.
  \item $L$ associates with each internal gate $g$ a function $L(g):
    \ind(\Sigma(g)) \rightarrow G$ such that if we define a relation $W
    \subseteq G^{2}$ by $W(h_1,h_2)$ iff $h_2$ is an internal gate and $h_1$ is
    in the image of $L(h_2)$, then $(G, W)$ is a directed acyclic graph.
  \end{itemize}
\end{definition}

@@

\begin{lem}
  Let $C$ be a circuit of order $n$, $\sigma \in \sym_n$ and $\pi, \pi' \in
  \aut(C)$ both extend $\sigma$, then for every gate $g$ in the circuit we have
  that $\pi (g)$ and $\pi'(g)$ are syntactically-equivalent.
  \label{lem:permutation-extending-syntactic-equivalence}
\end{lem}
\begin{proof}
  We first note that, from the definition of an automorphism, for any gate $g$
  in $C$, $\Sigma (g) = \Sigma (\pi (g)) = \Sigma (\pi' (g))$, and either all of
  $g$, $\pi (g)$ and $\pi (g')$ are output gates and $\pi (g) = \pi \Omega
  (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ or $\pi' (g)$ are output
  gates.

>>>>

\begin{definition}[Circuits on Structures]
  Let $\mathbb{B}$ be a basis and $\rho$ be a relational vocabulary, we define a
  \emph{$(\mathbb{B}, \rho)$-circuit} $C$ of order $n$ computing a $q$-ary query
  $Q$ as a structure $\langle G, \Omega, \Sigma, \Lambda, L \rangle$.
  \begin{myitemize}
    \setlength\itemsep{0mm}
  \item $G$ is called the set of gates of
    $C$.% and $\vert C \vert := \vert G \vert$.
  \item $\Omega$ is an injective function from $[n]^q$ to $G$. The gates in the
    image of $\Omega$ are called the output gates. When $q = 0$, $\Omega$ is a
    constant function mapping to a single output gate.
  \item $\Sigma$ is a function from $G$ to $\mathbb{B} \uplus \rho \uplus
    \{0,1\} $ such that $\vert \Sigma^{-1} (0) \vert \leq 1$ and $\vert
    \Sigma^{-1} (1) \vert \leq 1$. Those gates mapped to $\rho \uplus \{0,1\}$
    are called input gates, with those mapped to $\rho$ called relational gates
    and those mapped to $\{0,1\}$ called constant gates. Those gates mapped to
    $\mathbb{B}$ are called internal gates.
  \item $\Lambda$ is a sequence of injective functions $(\Lambda_{R_i})_{R_i \in
      R}$ such that $\Lambda_{R_i}$ maps each relational gate $g$ with $\Sigma
    (g) = R_i$ to the tuple $\Lambda_{R_i} (g) \in [n]^{r}$. When no ambiguity
    arises we write $\Lambda (g)$ for $\Lambda_{R_i} (g)$.
  \item $L$ associates with each internal gate $g$ a function $L(g):
    \ind(\Sigma(g)) \rightarrow G$ such that if we define a relation $W
    \subseteq G^{2}$ by $W(h_1,h_2)$ iff $h_2$ is an internal gate and $h_1$ is
    in the image of $L(h_2)$, then $(G, W)$ is a directed acyclic graph.
  \end{myitemize}
\end{definition}

@@

\begin{lem}
  Let $C$ be a circuit of order $n$, $\sigma \in \sym_n$ and $\pi, \pi' \in
  \aut(C)$ both extend $\sigma$, then for every gate $g$ in the circuit we have
  that $\pi (g)$ and $\pi'(g)$ are syntactically-equivalent.
  \label{lem:permutation-extending-syntactic-equivalence}
\end{lem}
\begin{proof}
  We first note that, from the definition of an automorphism, for any gate $g$
  in $C$, $\Sigma (g) = \Sigma (\pi (g)) = \Sigma (\pi' (g))$, and either all of
  $g$, $\pi (g)$ and $\pi (g')$ are output gates and $\pi (g) = \pi \Omega
  (\Omega^{-1}(g)) = \Omega (\sigma \Omega^{-1}(g)) = \pi' \Omega
  (\Omega^{-1}(g)) = \pi'(g)$, or none of $g$, $\pi(g)$ and $\pi' (g)$ are output
  gates.
